%%%%%%%%%%%%%%%%
%% Preambule  %%
%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{upgreek}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{scrextend}

\usepackage[all]{xy}
\usepackage{tikz-qtree}
\usepackage[margin=2.5cm]{geometry}

\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{subcaption}

\setlength{\parindent}{0pt}

\pagestyle{fancy}

\lhead{\opdrachtNaam\ \opdrachtNummer}
\rhead{\naam(\studentNummer)}
\rfoot{Page\ \thepage\ of\ \pageref{LastPage}}
\lfoot{\datum}
\cfoot{Fuzzy Logic}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}


%%%%%%%%%%%%%%%%
%%  Gegevens  %%
%%%%%%%%%%%%%%%%

\newcommand{\naam}          {Stefan Schenk}
\newcommand{\studentNummer} {11881798}
\newcommand{\opdrachtNaam}  {Assignment}
\newcommand{\opdrachtNummer}{3}
\newcommand{\datum}         {December 2017}


\begin{document}

%%%%%%%%%%%%%%%%
%% Question 1 %%
%%%%%%%%%%%%%%%%
\section{The Concepts of Precisiation and Cointension}
\input{src/question1}


%%%%%%%%%%%%%%%%
%% Question 2 %%
%%%%%%%%%%%%%%%%
\newpage
\section{On the Fundamental Differences Between Interval Type-2 and Type-1 Fuzzy Logic Controllers}
\input{src/question2}

%%%%%%%%%%%%%%%%
%% Bibliograp %%
%%%%%%%%%%%%%%%%
\newpage
\begin{thebibliography}{9}

\bibitem{lecture_5_uncertainty}
    A. Bilgin,
    \href{https://drive.google.com/uc?id=1j505Rpb5mCb6EVXmwBEv5caM-nmYwecJ&authuser=0&export=download}{Lecture 5 - Uncertainty, human reasoning and linguistic modelling}, Amsterdam, 2017.

\bibitem{lecture_6_types_of_fl_and_t2_fs}
    A. Bilgin,
    \href{https://drive.google.com/uc?id=1cKJrc8KOdRhiMGHUycb2IEiU2ZFiOgsZ&authuser=0&export=download}{Lecture 6 - Types of FL and T2 FS}, Amsterdam, 2017.

\bibitem{differences_between_it2_and_it1}
    D. Wu,
    \href{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=6145645}{”On the Fundamental Differences Between Interval Type-2 and Type-1 Fuzzy Logic Controllers”}, in IEEE Transactions on Fuzzy Systems, vol. 20, no. 5, pp. 832-848, Oct. 2012. doi: 10.1109/TFUZZ.2012.2186818.

\bibitem{concept_of_cointensive_precisiation}
    L.A. Zadeh,
    \href{http://www.math.s.chiba-u.ac.jp/~yasuda/open2all/Paris06/IPMU2006/HTML/FINALPAPERS/P703.PDF}{"The Concept of Cointensive Precisiation - A key to Mechanization of Natural Language Understanding"}.

\bibitem{is_there_a_need_for_fuzzy_logic}
    L.A. Zadeh,
    \href{http://www.sciencedirect.com/science/article/pii/S0020025508000716}{"Is there a need for fuzzy logic?"}, In Information Sciences, Volume 178, Issue 13, 2008, Pages 2751-2779, ISSN 0020-0255.

\end{thebibliography}

\end{document}
